---
title: "team"
author: "Zihao Han;Hongsheng Yin"
date: "March 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
library(dplyr)
library(tidyr)
defClean <- read_excel('C://Users//h8438//DSProject//ds202_lab4//cyclonesFootball2018.xlsx', sheet='Defensive')
offClean <- read_excel('C://Users//h8438//DSProject//ds202_lab4//cyclonesFootball2018.xlsx', sheet='Offensive')
bioClean <- read_excel('C://Users//h8438//DSProject//ds202_lab4//cyclonesFootball2018.xlsx', sheet='Biography')
defClean$Name <- as.factor(defClean$Name)
defClean$Opponent_Opponent <- as.factor(defClean$Opponent_Opponent)
offClean$Name <- as.factor(offClean$Name)
offClean$Opponent_Opponent <- as.factor(offClean$Opponent_Opponent)
bioClean$Name <- as.factor(bioClean$Name)
defClean <- defClean %>% mutate(
  Tackles_Solo = as.numeric(Tackles_Solo), Tackles_ASST = as.numeric(Tackles_ASST),
  Tackles_TFL = as.numeric(Tackles_TFL), Tackles_Sack = as.numeric(Tackles_Sack),
  Turnover_FF = as.numeric(Turnover_FF), Turnover_FR = as.numeric(Turnover_FR),
  Turnover_INT = as.numeric(Turnover_INT), Pass_QBH = as.numeric(Pass_QBH),
  Pass_PB = as.numeric(Pass_PB)
)
offClean <- offClean %>% mutate(
  Receiving_REC = as.numeric(Receiving_REC), Receiving_YDS = as.numeric(Receiving_YDS),
  Receiving_TD  = as.numeric(Receiving_TD), Rushing_ATT = suppressWarnings(as.numeric(Rushing_ATT)),
  Rushing_YDS = suppressWarnings(as.numeric(Rushing_YDS)), Rushing_TD = suppressWarnings(as.numeric(Rushing_TD)),
  `Passing_CMP-ATT` = suppressWarnings(as.numeric(`Passing_CMP-ATT`)), 
  Passing_YDS = suppressWarnings(as.numeric(Passing_YDS)),
  Passing_TD  = suppressWarnings(as.numeric(Passing_TD)), Passing_INT = suppressWarnings(as.numeric(Passing_INT))
)
bioClean <- bioClean %>% mutate(
  Weight = as.numeric(Weight)
)
str(defClean)
defClean
str(offClean)
str(bioClean)
```
#Part 2
##1
```{r}

defClean%>% gather(key = "Statistic",value = "count",3:11)
defClean<-defClean%>% gather(key = "Statistic",value = "count",3:11)
str(defClean)
defClean
```
##2
```{r}

library(ggplot2)
ggplot(defClean,aes(x=count))+geom_histogram()+facet_wrap(~Statistic,scales="free_x")

```
#### according to the graph, the take Turnover_FF, Turnover_FR, Turnover_INT is rare since their count is a few (only have 1 and the bar is low).

##3
```{r}
defClean%>% filter(Statistic=="Tackles_Solo",Opponent_Opponent%in%c("West Virginia","Kansas State"))%>%
   spread(Opponent_Opponent,count)%>%ggplot(aes(x=`West Virginia`,y=`Kansas State`))+geom_point()


defClean %>% spread(Statistic,count)%>%
   select(Name,Tackles_Solo,Opponent_Opponent)%>%
  filter(Opponent_Opponent%in%c("West Virginia","Kansas State"))%>%
  spread(Opponent_Opponent,Tackles_Solo)%>%
  ggplot(aes(x=`West Virginia`,y=`Kansas State`))+geom_point()


```
#### No, the number shows that in the scatterplot ,`Kansas State` get higher number( highter score) than `West Virginia`.


##4
```{r}
bioClean%>%separate(Hometown,into=c("City","State"), ",")
```

##5
```{r}
bioClean%>%separate(Hometown,into=c("City","State"),",")%>%count(State)%>%group_by(State)
```
#Part 3
##1
```{r}
full_join(offClean,bioClean)
```
##2
```{r}
full_join(offClean,bioClean)%>%ggplot(aes(x=Weight,y=Receiving_YDS))+geom_point()
```
#### THere is no relationship. In the graph only pople has 225 weight have higher Receiving_YDS score, outher weight have no sepcific relation.

##3
